Prag Bat

### 2020-11-25 analysis/data_round2.Rmd
add file for reli sensu rouder and haaf

data <- task_data %>%
  left_join(log)%>%
  filter(status == "keep")%>%
  mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
         subage = factor(as.numeric(substr(age,1,1))),
         trial = as.numeric(trial))%>%
  mutate(trial = ifelse(test_day == "2", 
                        ifelse(task == "card_sorting", trial + 6, trial +5),
                        trial),
         z_age = age - mean(age),
         z_trial = trial - mean(trial),
         item = ifelse(task == "card_sorting", sample,leftObject) )%>%
    select(id, test_day, subage,age, task,item, trial, correct, z_age, z_trial)

@@

```{r}
item_info <- data_frame(
  task = c(rep("mutual_exclusivity",10),rep("simple_inf",10),rep("ad_hoc_implicature",10)),
  trial = c(rep(1:10,3)), 
  item = c(rep(c("carrot","garlic","eggplant","duck","horseshoe"),2),rep(c("bear","robot","rocket","truck","dino"),2), rep(c("box","chair","table","plate","house"),2))
)

@@

data %>%
  filter(task == "mutual_exclusivity" |
         task == "simple_inf" |
         task == "ad_hoc_implicature",
         id %in% retest_ids)%>%
  select(-agent, -z_age, -z_trial)%>%
  left_join(item_info)%>%
  select(id, test_day, subage, age, age_month, task, trial, item, correct )%>%
  mutate(c_age_month = age_month - min(age_month),
         c_age = age - min(age))%>%
  write_csv("../../../Spin-off/spin-off/data/data.csv")
```

>>>>

data <- task_data %>%
  left_join(log)%>%
  filter(status == "keep")%>%
  mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
         subage = factor(as.numeric(substr(age,1,1))),
         trial = as.numeric(trial))%>%
  mutate(trial = ifelse(test_day == "2", 
                        ifelse(task == "card_sorting", trial + 6, trial +5),
                        trial),
         z_age = age - mean(age),
         z_trial = trial - mean(trial),
         item = ifelse(task == "card_sorting", sample, ifelse(task == "discourse_continuity", target1, leftObject)))%>%
    select(id, test_day, subage,age,age_month, task,item, trial, correct, z_age, z_trial)

@@

```{r}
item_info <- data_frame(
  task = c(rep("mutual_exclusivity",10),rep("simple_inf",10),rep("ad_hoc_implicature",10),rep("discourse_continuity",10),rep("card_sorting",12)),
  trial = c(rep(1:10,4),1:12), 
  item2 = c(rep(c("carrot","garlic","eggplant","duck","horseshoe"),2),rep(c("bear","robot","rocket","truck","dino"),2), rep(c("box","chair","table","plate","house"),2),rep(NA,22))
)

@@

data %>%
  filter(id %in% retest_ids)%>%
  select(-z_age, -z_trial)%>%
  left_join(item_info)%>%
  mutate(item = ifelse(task == "mutual_exclusivity" | task == "simple_inf" | task == "ad_hoc_implicature", item2,item))%>%
  select(id, test_day, subage, age, age_month, task, trial, item, correct )%>%
  mutate(c_age_month = age_month - min(age_month),
         c_age = age - min(age))%>%
  write_csv("../../../Spin-off/spin-off/data/data.csv")
```

### 2020-11-25 analysis/reliability.Rmd
add both data files from r1 and r2 to reliability analysis
add file for reli sensu rouder and haaf

library(tidyverse)
library(brms)
```

@@

data <- read_csv("../data/data.csv")

@@

```{r}
data%>%
  group_by(subage)%>%
  summarise(n= length(unique(id)))%>%
  kable()

@@

```{r}
data %>%
  group_by(subage,id)%>%
  summarise(testdays = length(unique(test_day)))%>%
  filter(testdays == 2)%>%
  summarise(complete_retest_data = length(id))%>%
  kable()
```

```{r}
# data %>%
#   group_by(id,test_day)%>%
#   summarise(n())%>%
#   arrange(id,test_day)

@@

```{r}
# data%>%
#   group_by(test_day,task)%>%
#   summarise(n= length(unique(id)))
```

## correlations

```{r}
# card sorting

complete_data <- reli_data %>%
  group_by(subage,id)%>%
  summarise(testdays = length(unique(test_day)))%>%
  filter(testdays == 2)%>%
  pull(id)

reli_data <- data%>%
  filter(task != "training", 
         id %in% complete_data)%>%
  mutate(test_day = ifelse(test_day == 1, "day1", "day2"))

rel_model <- brm(correct ~ (test_day|task/id),
                 data = reli_data, 
                 family = bernoulli(),
                 control = list(adapt_delta = 0.9),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = F,
          iter = 2000)

task <- as_tibble(ranef(rel_model)$task, rownames = "task")%>%
  select(task,Estimate.Intercept, Estimate.test_dayday2)%>%
  rename("Day1_int" = Estimate.Intercept,
         "Day2_int" = Estimate.test_dayday2)%>%
  mutate(task = str_replace(task, "card_sorting", "cardsorting"),
         task = str_replace(task, "mutual_exclusivity", "mutualexclusivity"))

id <- as_tibble(ranef(rel_model)$`task:id`, rownames = "id")%>%
  select(id,Estimate.Intercept, Estimate.test_dayday2)%>%
  rename("Day1" = Estimate.Intercept,
         "Day2" = Estimate.test_dayday2)%>%
  mutate(id = str_replace(id, "card_sorting", "cardsorting"),
         id = str_replace(id, "mutual_exclusivity", "mutualexclusivity"),
         Day1 = plogis(Day1),
         Day2 = plogis(Day2))%>%
  separate(id, c("task", "id"), sep = "_")

left_join(id, task)%>%
  mutate(est_1 = plogis(Day1_int + Day1),
         est_2 = plogis(Day2_int + Day2))%>%
  group_by(task)%>%
  summarise(cor = cor(est_1, est_2))

@@

## reliability

```{r}
# card sorting

cor_model <- brm(correct ~ 1 + (task|id) + (task|item),
                    data = data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 2000)

summary(cor_model)

>>>>

library(tidyverse)
library(brms)
library(tidybayes)
library(ggpubr)
```

@@

data <- bind_rows(
data_r1 <- read_csv("../data/data_r1.csv")%>%mutate(id = paste(id,"r1",sep = "_")) ,
data_r2 <- read_csv("../data/data_r2.csv")%>%mutate(id = paste(id,"r2",sep = "_"))
)%>%
  filter(task !="training")

@@

```{r}
data %>%
  group_by(task,id)%>%
  summarise(testdays = length(unique(test_day)))%>%
  filter(testdays == 2)%>%
  summarise(complete_retest_data = length(id))
```

# Simple correaltions

```{r}
reli <- data%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  group_by(task)%>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

reli
```

```{r}
p_rel_data <- data%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("day1" = `1`,
         "day2" = `2`)

ggplot(p_rel_data, aes(x = day1, y = day2))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(alpha = .5)+
  facet_wrap( ~ task)+
  stat_cor(method = "pearson",  aes(x = day1, y = day2), size = 2)+
  theme_minimal()+
  theme(aspect.ratio = 1)
```

## Combined model

```{r}
complete_data <- data %>%
  group_by(subage,id)%>%
  summarise(testdays = length(unique(test_day)))%>%
  filter(testdays == 2)%>%
  pull(id)

reli_data <- data%>%
  filter(task != "training", 
         id %in% complete_data)%>%
  mutate(test_day = ifelse(test_day == 1, "day1", "day2"),
         z_trial = scale(trial))

rel_model <- brm(correct ~ (1|test_day) + (1| task) + (1|id),
                 data = reli_data, 
                 family = bernoulli(),
                 control = list(adapt_delta = 0.9),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = F,
          iter = 5000)

draws1 <- rel_model %>%
  spread_draws(b_Intercept, day[test_day,], task[`test_day:test_day`,],id[`test_day:test_day:id`,])
#   separate(id, c("id","round"), sep = "_", extra = "merge")
# 
# draws2 <- rel_model %>%
#   spread_draws(b_Intercept,`r_id:test_day`[`id:test_day`,])%>%
#   separate(`id:test_day`, c("id","go"), sep = "_", extra = "merge")%>%
#   separate(go, c("round","day"), sep = "_", extra = "merge")
# 
# draws3 <- rel_model %>%
#   spread_draws(b_Intercept,`r_id:test_day:task`[`id:test_day:task`,])%>%
#   separate(`id:test_day:task`, c("id","go"), sep = "_", extra = "merge")%>%
#   separate(go, c("round","go"), sep = "_", extra = "merge")%>%
#   separate(go, c("day","task"), sep = "_", extra = "merge")
# 
# draws <- draws1 %>%
#   left_join(draws2) %>%
#   left_join(draws3)

p_re_est <- draws1%>%
  mutate(perf = b_Intercept + r_id + r_test_day + r_task)%>%
  group_by(id, test_day,task )%>%
  median_qi(perf)%>%
  mutate(perf = plogis(perf))

saveRDS(p_re_est,"../saves/p_re_est.rds")

p_data <- data %>%
  filter(id %in% complete_data)%>%
  group_by(task, test_day,id)%>%
  summarise(mean = mean(correct))%>%
  mutate(day = paste("day",test_day,sep = ""))

ggplot()+
  geom_point(data = p_re_est, aes (x = id, y = perf), alpha = .5)+
  geom_point(data = p_data, aes (x = id, y = mean), alpha = .5, col = "firebrick")+
  facet_grid(day~task)+
  theme_minimal()

p_cor <- p_re_est %>%
  select(task, id, test_day,perf)%>%
  spread(test_day, perf)%>%
  group_by(task)%>%
  summarise(cor = cor(day1, day2))%>%
  left_join(reli)

p_re_est %>%
  select(task, id, test_day,perf)%>%
  spread(test_day, perf)%>%
  ggplot(aes(x = day1, y = day2))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(alpha = .5)+
  geom_point(data = p_rel_data, aes(x = day1, y = day2), alpha = .5, col = "firebrick")+
  facet_wrap( ~ task)+
  stat_cor(method = "pearson",  aes(x = day1, y = day2), size = 2)+
  theme_minimal()+
  theme(aspect.ratio = 1)

```
# Ignore below 
## Separate models

```{r}
reli_data_1 <- reli_data%>%
  filter(test_day == "day1")

rel_model_1 <- brm(correct ~ (z_trial|id/task),
                 data = reli_data_1, 
                 family = bernoulli(),
                 control = list(adapt_delta = 0.9),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = F,
          iter = 5000)

summary(rel_model_1)

draws_rel1_1 <- rel_model_1 %>%
  spread_draws(b_Intercept,r_id[id,])%>%
  separate(id, c("id","round"), sep = "_", extra = "merge")

draws_rel1_2 <- rel_model_1 %>%
  spread_draws(b_Intercept,`r_id:task`[`id:task`,])%>%
  separate(`id:task`, c("id","go"), sep = "_", extra = "merge")%>%
  separate(go, c("round","task"), sep = "_", extra = "merge")

draws_rel1 <- draws_rel1_1 %>%
  left_join(draws_rel1_2)%>%
  mutate(perf = b_Intercept + r_id + `r_id:task`)%>%
  group_by(id,task )%>%
  median_qi(plogis(perf))%>%
  mutate(day1 = `plogis(perf)`)

@@

```{r}
reli_data_2 <- reli_data%>%
  filter(test_day == "day2")

rel_model_2 <- brm(correct ~ (z_trial|id/task),
                 data = reli_data_2, 
                 family = bernoulli(),
                 control = list(adapt_delta = 0.9),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = F,
          iter = 5000)

summary(rel_model_2)

draws_rel2_1 <- rel_model_2 %>%
  spread_draws(b_Intercept,r_id[id,])%>%
  separate(id, c("id","round"), sep = "_", extra = "merge")

draws_rel2_2 <- rel_model_2 %>%
  spread_draws(b_Intercept,`r_id:task`[`id:task`,])%>%
  separate(`id:task`, c("id","go"), sep = "_", extra = "merge")%>%
  separate(go, c("round","task"), sep = "_", extra = "merge")

draws_rel2 <- draws_rel2_1 %>%
  left_join(draws_rel2_2)%>%
  mutate(perf = b_Intercept + r_id + `r_id:task`)%>%
  group_by(id,task )%>%
  median_qi(plogis(perf))%>%
  mutate(day2 = `plogis(perf)`)

@@

```{r}
p_cor %>%left_join(
  draws_rel1 %>%
  select(id, task, day1)%>%
  left_join(draws_rel2%>%
  select(id, task, day2))%>%
    group_by(task)%>%
    summarise(cor_2_models = cor(day1, day2))
    )

@@

```{r}
draws_rel1 %>%
  select(id, task, day1)%>%
  left_join(draws_rel2%>%
  select(id, task, day2))%>%
  ggplot(aes(x = day1, y = day2))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(alpha = .5)+
  geom_point(data = p_rel_data, aes(x = day1, y = day2), alpha = .5, col = "firebrick")+
  facet_wrap( ~ task)+
  stat_cor(method = "pearson",  aes(x = day1, y = day2), size = 2)+
  theme_minimal()+
  theme(aspect.ratio = 1)
```
